Approximation as Differentiation

### 2025-04-29 appendix/notes/auto-diff.tex
Tangent map.

Write $\tangents_x(\RR^n)$ for the tangent space at a point $x \in \RR^n$. Then the \emph{forward derivative}
${\pushf{f}}_x$ (tangent map or pushforward) of a function $f: \RR^m \to \RR^n$ at $x$ is a linear map
$\tangents_x(\RR^m) \linearto \tangents_{f(x)}(\RR^n)$. Because $\RR^n$ is a Euclidean manifold,
$\tangents_x(\RR^n)$ is naturally isomorphic to $\RR^n$.

>>>>

Write $\tangents_x(\RR^n)$ for the tangent space at a point $x \in \RR^n$. Then the \emph{forward derivative}
${\pushf{f}}_x$ (tangent map or pushforward) of a differentiable function $f: \RR^m \to \RR^n$ at $x$ is a
linear map $\tangents_x(\RR^m) \linearto \tangents_{f(x)}(\RR^n)$. Because $\RR^n$ is a Euclidean manifold,
$\tangents_x(\RR^n)$ is naturally isomorphic to $\RR^n$, so ${\pushf{f}}_x: $\RR^m \linearto \RR^n$.
